Poseidon Adventure

### 2019-09-30 docs/index.Rmd
add climate run end to end to index
clarify what works and doesnt

>>>>

The below generates a readable dat file for input into SS3 for sardines. The control file and biological parameters are still a work in progress.

<a href="https://sgaichas.github.io/poseidon-dev/SardinesHakeatlantisom2SStest.html" target="_blank">Sardines in the CalCurrent run with F, rec dev, and climate scenario, all true and SS data, Sept 30, 2019</a>
